### 2015-11-10 TeachingStatement/main.tex
Tried to rework last paragraph

\section{Conclusions}
The best way to communicate information is on the receiver's
terms, regardless of if the context is teaching or research.
As such developing better methods for reaching both specific
individuals and broad audiences is essential to my career goals.
\end{document}

>>>>

\section{Future Goals}
While much of my teaching experience has been with introductory
programming courses, I am also interested in teaching higher level
and theory based courses. Artificial intelligence and machine learning
are common courses which coincide strongly with my research interests.
Algorithms, discrete math, and graph theory are topics that I believe
present exciting challgenges for keeping students engaged.
From previous work I have also acquired significant knowledge of
introductory and high performance C++ and would enjoy teaching classes
on those topics.

The best way to communicate information is on the receiver's
terms, regardless of if the context is teaching or research.
As such developing better methods for reaching both specific
individuals and broad audiences is essential to my career goals,
and is something I plan to continue improving.
\end{document}
